Supplemental Materials for: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-22 supp.Rmd
Corrected ARR code

# Calculate the effect sizes
data_CS1a<-data_CS1a %>% 
              mutate(ARR=(mean_high_f-mean_low_f)/(acc_temp_high - acc_temp_low),
                     Var_ARR=((1/(acc_temp_high-acc_temp_low))^2*(sd_low_f^2/n_low_f_adj+sd_high_f^2/n_high_f_adj)))

@@

```{r, class.source='klippy', results = 'hide'}
data_CS1b<-data_CS1b %>% # calculate effect sizes

  mutate(ARR_f=((mean_high_f-mean_low_f)/(acc_temp_high-acc_temp_low))) %>% 
  mutate(ARR_m=((mean_high_m-mean_low_m)/(acc_temp_high-acc_temp_low))) %>% 
  mutate(ARRD=ARR_f - ARR_m) %>% 
  mutate(Var_ARRD=((1/(acc_temp_high-acc_temp_low))^2*(sd_low_f^2/n_low_f_adj+sd_high_f^2/n_high_f_adj+sd_low_m^2/n_low_m_adj+sd_high_m^2/n_high_m_adj)))

# Remove dependent effect sizes
data_CS1b<-filter(data_CS1b,
                    es_ID!="es85"&
                    es_ID!="es86"&
                    es_ID!="es87"&
                    es_ID!="es98")
```

>>>>

# Calculate the effect sizes
data_CS1a<-data_CS1a %>% 
              mutate(ARR=(mean_high-mean_low)/(acc_temp_high - acc_temp_low),
                     Var_ARR=((1/(acc_temp_high-acc_temp_low))^2*(sd_low^2/n_low_adj+sd_high^2/n_high_adj)))

@@

# calculate effect sizes
data_CS1b<-data_CS1b %>% 
  mutate(ARR_f=((mean_high_f-mean_low_f)/(acc_temp_high-acc_temp_low)),
         ARR_m=((mean_high_m-mean_low_m)/(acc_temp_high-acc_temp_low)),
         ARRD= ARR_f - ARR_m,
         Var_ARRD=((1/(acc_temp_high-acc_temp_low))^2*(sd_low_f^2/n_low_f_adj+sd_high_f^2/n_high_f_adj+sd_low_m^2/n_low_m_adj+sd_high_m^2/n_high_m_adj)))

# Remove dependent effect sizes
data_CS1b <- filter(data_CS1b,
                    es_ID!="es85"&
                    es_ID!="es86"&
                    es_ID!="es87"&
                    es_ID!="es98")
```
